|

### 2021-10-24 article/articleCustomerDropoutMembership.Rmd
upd

``` {.markdown}
If an organization can predict a possible dropout and
develop countermeasures to avoid desertion, they can avoid customer defections that 
lead to a loss of money. Reichheld (1996) evidenced that reducing dropout rates by 5% 
(e.g., from 15% to 10% per year) could represent an increase in prots up to double, as 
acquiring new customers costs 5 to 6 times more than retaining existing ones (Bhattacharya, 
1998). Existing organizations are addressing this problem by shifting their target from 
capturing new customers to preserving existing ones (García et al., 2017),
as investments in retention strategies have higher returns than acquisitions (Coussement 
& Van den Poel, 2009). The importance of customer retention to maintain organizational protability (Devriendt
et al., 2019) leads to the problem of how to quantify the nancial impact of customer retention actions
under the assumption that the organization goal should be related to the increase the lifetime of the
customer to increase their prots. The customer lifetime value (CLV) allows us to measure this, as itr
```

@@

There are several challenges around the timing related to dropout, or
considering the dynamic behavior of the customer in the intent to drop out
[@alboukaey_dynamic_2020]. The importance of understanding when dropout will
occur and the risk when discarding the temporal perspective of the problem seems
to be an element that should be addressed. Few studies considered this
[@perianez_churn_2016; @burez_separating_2008]. This shows an opportunity to
address the importance of the timeframe and its influence on the efficiency of
the model and also evalute if the combination of clusters could improve the
performance.

@@

```{python createModel, eval=FALSE, echo=FALSE, cache = FALSE, warning = FALSE}
from pysurvival.models.survival_forest import RandomSurvivalForestModel
from sklearn.model_selection import train_test_split
from pysurvival.utils.metrics import concordance_index
from pysurvival.utils.display import integrated_brier_score
from pysurvival.utils.display import compare_to_actual

@@

# Fitting the model
csf = RandomSurvivalForestModel(num_trees=200)
csf.fit(X_train, t_train, e_train, max_features='sqrt', max_depth=5, min_node_size=20)

@@

```{python createModelClusters, eval=TRUE, echo=FALSE, cache = TRUE, warning = FALSE}
# Building training and testing sets for the clusters
for cluster in df_members.cluster.unique():
    # Number of samples in the dataset
    df_members_cluster = df_members[df_members.cluster == cluster]
    X = df_members_cluster.copy()
    t = df_members_cluster['years_membership']
    e = df_members_cluster['dropout']
    X.drop(axis=1, columns=['years_membership','dropout'])
    X_train, X_test, t_train, t_test, e_train, e_test = train_test_split(X, t, e, random_state=0)
    print(f"The cluster {cluster} as a size of {X.shape[0]}")
    # Fitting the model
    csf = RandomSurvivalForestModel(num_trees=200)
    csf.fit(X_train, t_train, e_train, max_features='sqrt',
        max_depth=5, min_node_size=20)

@@

There are several challenges around the timing related to dropout, or
considering the dynamic behavior of the customer in the intent to drop out
[@alboukaey_dynamic_2020]. The importance of understanding when dropout will
occur and the risk when discarding the temporal perspective of the problem seems
to be an element that should be addressed. Few studies considered this
[@perianez_churn_2016; @burez_separating_2008]. This shows an opportunity to
address the importance of the timeframe and its influence on the efficiency of
the model.

@@

From RQ5, the literature analysis showed that different types of questions
arise. Which are the best approaches to develop the analysis of the performance
in predicting dropout? Several metrics are customer dropout is to improve the
performance of organizations in retaining customers, which is a management
problem in which data mining is adopted [@verbeke_new_2012]. The goals of the
model should be formulated considering the context of the problem that is being
addressed; in marketing retention strategies, the up-lift supports the
development of proactive actions to minimize the investment in retention
strategies [@coussement_churn_2008]. Some assumptions that underlie the adoption
of uplift metrics consider that customers with a higher risk of churning could
not be the best targets, as suggested by @ascarza_retention_2018. Other
researchers addressed the problem using the top-decile lift to develop more
proactive actions to retain the customers at risk of churning
[@coussement_churn_2008;xie_customer_2009]. This approach considers the 10% of
customers with more risk, and investments in retention strategies should be
developed that distinguish the churners susceptible to marketing actions from
those who will leave anyway [@coussement_comparative_2017]. Although uplift
models seem to be good strategies, they should also used, such as AUC,
sensitivity, specificity, recall, precision, and F-score. However, the goal
ofconsider factors other than risk and customer satisfaction, as not taking this
into consideration could be counterproductive and the model should be removed
from the retention strategy.

@@

```{=latex}
\begin{table}[ht]
    \footnotesize
    \centering
    \begin{tabular}{p{0.15\textwidth}p{0.55\textwidth}p{0.25\textwidth}}
    \hline
    \textbf{Model name} & \textbf{Explored parameters values} & \textbf{Best parameters} \\
    \hline
    Survival trees  & pysurvival random forest                  & a \\
    Survival trees
    with clusters   & pysurvival random forest with clusters    & a \\
    Scikit survival 
    trees           & scikit survival                           & a \\
    Scikit survival 
    with clusters   & scikit with clusters                      & a \\
    Scikit survival 
    gradient boost  & scikit survival gradient boost            & a \\
    Scikit survival 
    gradient boost 
    with clusters   & scikit with clusters                      & a \\
    \hline
    \end{tabular}
    \caption{Hyper-parameters best values}
    \label{hyperparametersbestvalues}
\end{table}
```
```{=html}
<!--
|        Model name        | Explored hyper-parameters' values                    | Best parameters |
| ------------------------ | ---------------------------------------------------- | --------------- |
| Survival trees           |                                                      |                 |   
| without cluster          |                                                      |                 |  
-->
```

The results of the performance of the models are available in table 4.
Colocar o modelo. Resultados do modelo
```{=latex}
\begin{table}[ht]
    \footnotesize
    \centering
    \begin{tabular}{p{0.15\textwidth}p{0.55\textwidth}p{0.25\textwidth}}
    \hline
    \textbf{Model name} & \textbf{Results} \\
    \hline
    Survival trees  & RMSE 2.77 Median Absolute Error 0.0 \\
    Survival trees
    with clusters   & Cluster 1: RMSE  2.775 Median Absolute Error  0.000 
                      Cluster 3: RMSE  8.769 Median Absolute Error  1.276
                      Cluster 2: RMSE 14.883 Median Absolute Error  2.030
                      Cluster 4: RMSE  9.624 Median Absolute Error  4.748
                      Cluster 0: RMSE 77.236 Median Absolute Error 26.066 \\
    Scikit survival 
    trees           & scikit survival                           \\
    Scikit survival 
    with clusters   & scikit with clusters                      \\
    Scikit survival 
    gradient boost  & scikit survival gradient boost           \\
    Scikit survival 
    gradient boost 
    with clusters   & scikit with clusters                      \\
    \hline
    \end{tabular}
    \caption{Hyper-parameters best values}
    \label{hyperparametersbestvalues}
\end{table}
```
# Conclusion

@@

Example of Developed actions:

``` {.markdown}
Each month, the company identified the customers who were up for renewal and
split them (randomly and evenly) between a treatment group that received a 
"thank you" gift with the letter and a control group that received only the 
renewal latter.
```

>>>>

``` markdown
If an organization can predict a possible dropout and
develop countermeasures to avoid desertion, they can avoid customer defections that 
lead to a loss of money. Reichheld (1996) evidenced that reducing dropout rates by 5% 
(e.g., from 15% to 10% per year) could represent an increase in prots up to double, as 
acquiring new customers costs 5 to 6 times more than retaining existing ones (Bhattacharya, 
1998). Existing organizations are addressing this problem by shifting their target from 
capturing new customers to preserving existing ones (García et al., 2017),
as investments in retention strategies have higher returns than acquisitions (Coussement 
& Van den Poel, 2009). The importance of customer retention to maintain organizational protability (Devriendt
et al., 2019) leads to the problem of how to quantify the nancial impact of customer retention actions
under the assumption that the organization goal should be related to the increase the lifetime of the
customer to increase their prots. The customer lifetime value (CLV) allows us to measure this, as itr
```

@@

There are several challenges around the timing related to dropout, or
considering the dynamic behavior of the customer in the intent to drop out
\[@alboukaey_dynamic_2020\]. The importance of understanding when dropout will
occur and the risk when discarding the temporal perspective of the problem seems
to be an element that should be addressed. Few studies considered this
\[@perianez_churn_2016; @burez_separating_2008\]. This shows an opportunity to
address the importance of the timeframe and its influence on the efficiency of
the model and also evalute if the combination of clusters could improve the
performance.

@@

```{python createModel, eval=TRUE, echo=FALSE, cache = FALSE, warning = FALSE}
from pysurvival.models.survival_forest import RandomSurvivalForestModel
from sklearn.model_selection import train_test_split
from pysurvival.utils.metrics import concordance_index
from pysurvival.utils.display import integrated_brier_score
from pysurvival.utils.display import compare_to_actual

@@

# Fitting the model
csf = RandomSurvivalForestModel(num_trees=20)
csf.fit(X_train, t_train, e_train, max_features='sqrt', max_depth=5, min_node_size=20, seed = 1)

@@

```{python createModelClusters, eval=TRUE, echo=FALSE, cache = TRUE, warning = FALSE}
# Building training and testing sets for the clusters
for cluster in df_members.cluster.unique():
    # Number of samples in the dataset
    df_members_cluster = df_members[df_members.cluster == cluster]
    X = df_members_cluster.copy()
    t = df_members_cluster['years_membership']
    e = df_members_cluster['dropout']
    X.drop(axis=1, columns=['years_membership','dropout'])
    X_train, X_test, t_train, t_test, e_train, e_test = train_test_split(X, t, e, random_state=0)
    print(f"The cluster {cluster} as a size of {X.shape[0]}")
    # Fitting the model
    csf = RandomSurvivalForestModel(num_trees=20)
    csf.fit(X_train, t_train, e_train, max_features='sqrt',
        max_depth=5, min_node_size=20, seed = 1)

@@

There are several challenges around the timing related to dropout, or
considering the dynamic behavior of the customer in the intent to drop out
\[@alboukaey_dynamic_2020\]. The importance of understanding when dropout will
occur and the risk when discarding the temporal perspective of the problem seems
to be an element that should be addressed. Few studies considered this
\[@perianez_churn_2016; @burez_separating_2008\]. This shows an opportunity to
address the importance of the timeframe and its influence on the efficiency of
the model.

@@

From RQ5, the literature analysis showed that different types of questions
arise. Which are the best approaches to develop the analysis of the performance
in predicting dropout? Several metrics are customer dropout is to improve the
performance of organizations in retaining customers, which is a management
problem in which data mining is adopted \[@verbeke_new_2012\]. The goals of the
model should be formulated considering the context of the problem that is being
addressed; in marketing retention strategies, the up-lift supports the
development of proactive actions to minimize the investment in retention
strategies \[@coussement_churn_2008\]. Some assumptions that underlie the
adoption of uplift metrics consider that customers with a higher risk of
churning could not be the best targets, as suggested by @ascarza_retention_2018.
Other researchers addressed the problem using the top-decile lift to develop
more proactive actions to retain the customers at risk of churning
\[@coussement_churn_2008;xie_customer_2009\]. This approach considers the 10% of
customers with more risk, and investments in retention strategies should be
developed that distinguish the churners susceptible to marketing actions from
those who will leave anyway [@coussement_comparative_2017]. Although uplift
models seem to be good strategies, they should also used, such as AUC,
sensitivity, specificity, recall, precision, and F-score. However, the goal
ofconsider factors other than risk and customer satisfaction, as not taking this
into consideration could be counterproductive and the model should be removed
from the retention strategy.

@@

```{=latex}
\begin{table}[ht]
    \footnotesize
    \centering
    \begin{tabular}{p{0.15\textwidth}p{0.55\textwidth}p{0.25\textwidth}}
    \hline
    \textbf{Model name} & \textbf{Explored parameters values} & \textbf{Best parameters} \\
    \hline
    Survival trees  & pysurvival random forest                  & a \\
    Survival trees
    with clusters   & pysurvival random forest with clusters    & a \\
    Scikit survival 
    trees           & scikit survival                           & a \\
    Scikit survival 
    with clusters   & scikit with clusters                      & a \\
    Scikit survival 
    gradient boost  & scikit survival gradient boost            & a \\
    Scikit survival 
    gradient boost 
    with clusters   & scikit with clusters                      & a \\
    \hline
    \end{tabular}
    \caption{Hyper-parameters best values}
    \label{hyperparametersbestvalues}
\end{table}
```
The results of the performance of the models are available in table 4. Colocar o
modelo. Resultados do modelo

```{=latex}
\begin{table}[ht]
    \footnotesize
    \centering
    \begin{tabular}{p{0.15\textwidth}p{0.35\textwidth}r p{0.10\textwidth}}
    \hline
    \textbf{Model name} & \textbf{Results} & \textbf{n}\\
    \hline
    Survival trees  & RMSE 57.815                                     & 25316\\
                    & MAE 18.966                                      & \\   
                    & MEAE 38.557                                     & \\
    Survival trees  & Cluster 0: RMSE  2.785 MAE  0.000 MEAE  0.899   &   930\\
    with clusters   & Cluster 1: RMSE 78.141 MAE 28.537 MEAE 56.989   & 17067\\
                    & Cluster 2: RMSE 15.081 MAE  1.995 MEAE  6.850   &  2423\\
                    & Cluster 3: RMSE  9.354 MAE  2.506 MEAE  6.427   &  2816\\
                    & Cluster 4: RMSE  8.805 MAE  1.349 MEAE  3.725   &  2080\\

    Scikit survival 
    trees           & scikit survival                                 & \\
    Scikit survival 
    with clusters   & scikit with clusters                            & \\
    Scikit survival 
    gradient boost  & scikit survival gradient boost                  & \\
    Scikit survival 
    gradient boost 
    with clusters   & scikit with clusters                            & \\
    \hline
    \end{tabular}
    \caption{Hyper-parameters best values}
    \label{hyperparametersbestvalues}
    * Root Mean Square Error (RMSE), Mean Absolute Error (MAE), Median Absolute Error (MEAE)  
\end{table}
```
# Conclusion

@@

Example of Developed actions place in the discussion:

``` markdown
Each month, the company identified the customers who were up for renewal and
split them (randomly and evenly) between a treatment group that received a 
"thank you" gift with the letter and a control group that received only the 
renewal latter.
```
